The Astropy Project

### 2017-11-11 main.tex
some minor cleaning up

\subsection{Coordinates}
\label{sec:coordinates}
% Adrian, Erik

\subsubsection{Overview}
The \package{astropy.coordinates} subpackage is designed to support representing
and transforming celestial coordinates and, new in version 2.0, velocities.
The framework heavily relies on the \package{astropy.units} subpackage, and most
inputs to objects in this subpackage are expected to be \texttt{Quantity}
objects.
Some of the machinery also relies on the Essential Routines of Fundamental
Astronomy (ERFA) \texttt{C} library for some of the critical underlying
transformation machinery \citep{erfa}, which is based on the Standards Of
Fundamental Astronomy (SOFA) effort \citep{sofa}.

@@

@@

%\subsubsection{Accuracy and comparison of coordinate system definitions}
% Erik?

>>>>

\subsection{Coordinates}
\label{sec:coordinates}
% Adrian, Erik
The \package{astropy.coordinates} subpackage is designed to support representing
and transforming celestial coordinates and, new in version 2.0, velocities.
The framework heavily relies on the \package{astropy.units} subpackage, and most
inputs to objects in this subpackage are expected to be \texttt{Quantity}
objects.
Some of the machinery also relies on the Essential Routines of Fundamental
Astronomy (ERFA) \texttt{C} library for some of the critical underlying
transformation machinery \citep{erfa}, which is based on the Standards Of
Fundamental Astronomy (SOFA) effort \citep{sofa}.

@@

In what follows, we briefly highlight key new features in
\texttt{astropy.coordinates}.

@@
